Score-based tests of measurement invariance: Use in practice

### 2014-06-05 frontiers/IMPSpres-knitr.Rnw
update Rnw file chunk options format.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@340 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{frame}
\begin{figure}
\tiny{\caption{M.I.violation parameter $\lambda_{11}$.  Testing
    parameters are $\lambda_{11}$ and $\lambda_{11} \ldots \lambda_{62}$.}}
\label{fig:sim11res}
<<sim11res, fig=TRUE, height=5, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim1$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim1,
       subset = (parms == "loading" & 
          pars %in% c("Loading1", "All Loadings") & diff %% 0.5 == 0),
       type = "b", xlab = 
          expression(paste("Violation Magnitude (", lambda[11], ")")),
       ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
           if(which.given == 2){
             strip.default(which.given, factor.levels = 
                           parlabs[c(1, 5)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

\end{figure}
\end{frame}
%--------------------------------------------------------------------------
\begin{frame}
\begin{figure}
\tiny{\caption{M.I.violation parameter $\lambda_{11}$.  Testing
    parameters are $\psi_{11} \ldots \psi_{66}, \sigma_{12}$ and
    $\mu_{11} \ldots \mu_{66}$.}}
\label{fig:sim12res}
<<sim12res, fig=TRUE, height=5, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim1$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim1,
       subset = (parms == "loading" & 
          pars %in% c("All Errors", "Covariance", "All Intercepts") 
                 & diff %% 0.5 == 0),
       type = "b", xlab = 
          expression(paste("Violation Magnitude (", lambda[11], ")")),
       ylab = "Power", ylim = c(0,1), key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
           if(which.given == 2){
             strip.default(which.given, factor.levels = 
                           parlabs[c(2, 6, 7)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

@@

\node[error] (E1) at (7,6) {E1}
   edge [post] node[auto,swap]{\small{1}}(SCALE1)
   edge [errorsling, bend right=100]node[right=0.1,text width=2cm]
   {\scriptsize{$\psi_{11}=26.77$}} (E1.45);
\node[error] (E2) at (7,4.5) {E2}
   edge [post] node[auto,swap]{\small{1}} (SCALE2)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]
   {\scriptsize{$\psi_{22}=13.01$}}(E2.45);
\node[error] (E3) at (7,3) {E3}
   edge [post] node[auto,swap]{\small{1}}(SCALE3)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]
   {\scriptsize{$\psi_{33}=30.93$}}(E3.45);
\node[error] (E4) at (7,1) {E4}
   edge [post] node[auto,swap]{\small{1}}(SCALE4)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]
   {\scriptsize{$\psi_{44}=3.17$}}(E4.45);
\node[error] (E5) at (7,-0.5) {E5}
   edge [post] node[auto,swap]{\small{1}}(SCALE5)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]
   {\scriptsize{$\psi_{55}=8.82$}} (E5.45);
\node[error] (E6) at (7,-2) {E6}
   edge [post] node[auto,swap]{\small{1}}(SCALE6)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]
   {\scriptsize{$\psi_{66}=22.5$}}(E6.45);
\end{tikzpicture}}
\end{figure}
\end{frame}
%--------------------------------------------------------------------------
\begin{frame}
\begin{figure}
\tiny{\caption{The parameter violating measurement invariance is the 
    unmodeled loading. Testing parameters are $\lambda_{11}$ and $\psi_{11}$.}}
\label{fig:sim21res}
<<sim21res, fig=TRUE, height=5, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
       subset = (parms == "extra" & 
	 pars %in% c("Loading1", "Error1") 
                 & diff %% 0.5 == 0),
       type = "b", xlab = "Violation Magnitude (Unmodeled Loading)",
       ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	 strip.default(which.given, factor.levels = parlabs[c(1, 3)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@
\end{figure}
\end{frame}
%--------------------------------------------------------------------------
\begin{frame}
\begin{figure}
\tiny{\caption{The parameter violating measurement invariance is 
    the unmodeled loading. Testing parameters are $\sigma_{12}$ 
    and $\mu_{11}$.}}
\label{fig:sim22res}
<<sim22res, fig=TRUE, height=5, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
       subset = (parms == "extra" &
	 pars %in% c("Covariance", "Intercept1") 
                 & diff %% 0.5 == 0),
       type = "b", xlab = "Violation Magnitude (Unmodeled Loading)",
       ylab = "Power", ylim = c(0,1), key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	 strip.default(which.given, factor.levels = parlabs[c(2, 4)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@
\end{figure}
\end{frame}

@@

\begin{frame}
\begin{figure}
\tiny{\caption{Fluctuation processes for the $\mathit{WDM}_o$ statistic}}
\label{fig:ordres}
<<sctest-ord-graphics,fig=TRUE, height=3.3, width=5, echo=FALSE, results=hide>>=
sctest(restr, order.by = yg$agegroup, parm = 1:4, vcov = "info",
  functional = "WDMo", plot = TRUE, ylim = c(0, 3.2),
  xlab = "Age group", ylab = "Weighted test statistics",
  main = expression(WDM[o]), boundary = list(col = "red", lty = 1))
@
\end{figure}
\end{frame}
%--------------------------------------------------------------------------
\begin{frame}
 \begin{itemize}
 \item Thanks! 
 \item Questions?
 \end{itemize}
\end{frame}
%--------------------------------------------------------------------------
\end{document}

>>>>

\begin{frame}
\begin{figure}
\tiny{\caption{M.I.violation parameter $\lambda_{11}$.  Testing
    parameters are $\lambda_{11}$ and $\lambda_{11} \ldots \lambda_{62}$.}}
\label{fig:sim11res}
<<sim11res, fig.height=5, fig.width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim1$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim1,
       subset = (parms == "loading" & 
          pars %in% c("Loading1", "All Loadings") & diff %% 0.5 == 0),
       type = "b", xlab = 
          expression(paste("Violation Magnitude (", lambda[11], ")")),
       ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
           if(which.given == 2){
             strip.default(which.given, factor.levels = 
                           parlabs[c(1, 5)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

\end{figure}
\end{frame}
%--------------------------------------------------------------------------
\begin{frame}
\begin{figure}
\tiny{\caption{M.I.violation parameter $\lambda_{11}$.  Testing
    parameters are $\psi_{11} \ldots \psi_{66}, \sigma_{12}$ and
    $\mu_{11} \ldots \mu_{66}$.}}
\label{fig:sim12res}
<<sim12res, fig.height=5, fig.width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim1$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim1,
       subset = (parms == "loading" & 
          pars %in% c("All Errors", "Covariance", "All Intercepts") 
                 & diff %% 0.5 == 0),
       type = "b", xlab = 
          expression(paste("Violation Magnitude (", lambda[11], ")")),
       ylab = "Power", ylim = c(0,1), key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
           if(which.given == 2){
             strip.default(which.given, factor.levels = 
                           parlabs[c(2, 6, 7)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

@@

\node[error] (E1) at (7,6) {E1}
   edge [post] node[auto,swap]{\small{1}}(SCALE1)
   edge [errorsling, bend right=100]node[right=0.1,text width=2cm]
   {\scriptsize{$\psi_{11}=26.77$}} (E1.45);
\node[error] (E2) at (7,4.5) {E2}
   edge [post] node[auto,swap]{\small{1}} (SCALE2)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]
   {\scriptsize{$\psi_{22}=13.01$}}(E2.45);
\node[error] (E3) at (7,3) {E3}
   edge [post] node[auto,swap]{\small{1}}(SCALE3)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]
   {\scriptsize{$\psi_{33}=30.93$}}(E3.45);
\node[error] (E4) at (7,1) {E4}
   edge [post] node[auto,swap]{\small{1}}(SCALE4)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]
   {\scriptsize{$\psi_{44}=3.17$}}(E4.45);
\node[error] (E5) at (7,-0.5) {E5}
   edge [post] node[auto,swap]{\small{1}}(SCALE5)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]
   {\scriptsize{$\psi_{55}=8.82$}} (E5.45);
\node[error] (E6) at (7,-2) {E6}
   edge [post] node[auto,swap]{\small{1}}(SCALE6)
   edge [errorsling, bend right=100] node[right=0.1,text width=2cm]
   {\scriptsize{$\psi_{66}=22.5$}}(E6.45);
\end{tikzpicture}}
\end{figure}
\end{frame}
%--------------------------------------------------------------------------
\begin{frame}
\begin{figure}
\tiny{\caption{The parameter violating measurement invariance is the 
    unmodeled loading. Testing parameters are $\lambda_{11}$ and $\psi_{11}$.}}
\label{fig:sim21res}
<<sim21res, fig.height=5, fig.width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
       subset = (parms == "extra" & 
	 pars %in% c("Loading1", "Error1") 
                 & diff %% 0.5 == 0),
       type = "b", xlab = "Violation Magnitude (Unmodeled Loading)",
       ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	 strip.default(which.given, factor.levels = parlabs[c(1, 3)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@
\end{figure}
\end{frame}
%--------------------------------------------------------------------------
\begin{frame}
\begin{figure}
\tiny{\caption{The parameter violating measurement invariance is 
    the unmodeled loading. Testing parameters are $\sigma_{12}$ 
    and $\mu_{11}$.}}
\label{fig:sim22res}
<<sim22res, fig.height=5, fig.width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
       subset = (parms == "extra" &
	 pars %in% c("Covariance", "Intercept1") 
                 & diff %% 0.5 == 0),
       type = "b", xlab = "Violation Magnitude (Unmodeled Loading)",
       ylab = "Power", ylim = c(0,1), key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	 strip.default(which.given, factor.levels = parlabs[c(2, 4)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@
\end{figure}
\end{frame}

@@

\begin{frame}
\begin{figure}
\tiny{\caption{Fluctuation processes for the $\mathit{WDM}_o$ statistic}}
\label{fig:ordres}
<<sctest-ord-graphics, fig.height=3.3, fig.width=5, echo=FALSE, results='hide'>>=
sctest(restr, order.by = yg$agegroup, parm = 1:4, vcov = "info",
  functional = "WDMo", plot = TRUE, ylim = c(0, 3.2),
  xlab = "Age group", ylab = "Weighted test statistics",
  main = expression(WDM[o]), boundary = list(col = "red", lty = 1))
@
\end{figure}
\end{frame}
%--------------------------------------------------------------------------
\begin{frame}
 \begin{itemize}
 \item Thanks! 
 \item Questions?
 \end{itemize}
\end{frame}
%--------------------------------------------------------------------------
\end{document}
